\makeglossaries
\renewcommand*\glspostdescription{\dotfill}
\renewcommand{\glossarysection}[2][]{}
 
\newglossaryentry{gta5}
{
    name={Grand Theft Auto \rom{5}},
    description={Rockstar Games. 2013}
}

\newglossaryentry{starwars-tor}
{
	name={Star Wars: The Old Republic},
	description={Electronic Arts. 2011}
}

\newglossaryentry{destiny}
{
	name={Destiny},
	description={Activision. 2014}
}

\newglossaryentry{rogue}
{
	name={Rogue},
	description={Michael Toy, Glenn Wichman, Ken Arnold. 1980}
}

\newglossaryentry{angband}
{
	name={Angband},
	description={Alex Cutler, Andy Astrand. 1990}
}

\newglossaryentry{diablo}
{
	name={Diablo},
	description={Blizzard Entertainment. 1996}
}

\newglossaryentry{dwarffortress}
{
	name={Dwarf Fortress},
	description={Bay 12 Games. 2006}
}

\newglossaryentry{spelunky}
{
	name={Spelunky},
	description={Mossmouth. 2008}
}

\newglossaryentry{civ}
{
	name={Civilization},
	description={MicroProse. 1991}
}

\newglossaryentry{fireemblem}
{
	name={Fire Emblem},
	description={Nintendo. 1990}
}

\newglossaryentry{fft}
{
	name={Final Fantasy Tactics},
	description={Square. 1997}
}

\newglossaryentry{disgaea1}
{
	name={Disgaea: Hour of Darkness},
	text={Disgaea},
	description={Nippon Ichi Software. 2003}
}

\newglossaryentry{warcraft}
{
	name={Warcraft: Orcs \& Humans},
	text={Warcraft},
	description={Blizzard Entertainment. 1994}
}

\newglossaryentry{cnc}
{
	name={Command \& Conquer},
	description={Virgin Interactive. 1995}
}

\newglossaryentry{starcraft}
{
	name={Starcraft},
	description={Blizzard Entertainment. 1998}
}

\newglossaryentry{zog}
{
	name={Zillions of Games},
	description={Zillions Development Corp. 1998}
}

\newglossaryentry{yavalath}
{
	name={Yavalath},
	description={Cameron Browne. 2007}
}

\newglossaryentry{runescape}
{
	name={RuneScape},
	description={Jagex. 2001}
}